### 2023-06-06 manuscript.Rmd
removed whitespace
Update manuscript.Rmd
Co-authored-by: Aaron Peikert <aaron.peikert@posteo.de>

---
title             : "Assessing rigor and impact in research software"
#subtitle          : "Commentary: 'Responsible Research Assessment II: A specific proposal for hiring and promotion in psychology'"
shorttitle        : "Rigor and impact"

>>>>

---
title             : "Assessing rigor and impact of research software for hiring and promotion in psychology"
#subtitle          : "Commentary: 'Responsible Research Assessment II: A specific proposal for hiring and promotion in psychology'"
shorttitle        : "Rigor and impact"
